### 2018-07-02 Paper/Rebuttal/rebuttal.tex

\documentclass[12pt]{article}
\input{def}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{enumitem}

%\usepackage[left=0.75in ,top=0.5in, bottom=0.5in, right=0.75in, footskip=0.5cm]{geometry}
\begin{document}

\parskip=6pt

\begin{center}
{\bf Summary of Modifications to HMT\_2018\_2060}\\[6pt]
{\bf Uncertainty Quantification in Non-Equilibrium Molecular Dynamics Simulations of Thermal Transport}\\[6pt]
By \\
Manav Vohra, Ali Yousefzadi Nobakht, Seungha Shin, Sankaran Mahadevan 
\end{center}

\baselineskip=22pt

\vspace*{1in}

We thank the reviewers for their assessment of our manuscript.
Below is a summary of modifications made to our original submission in
response to the reviewers suggestions.

Where possible, key modifications have been highlighted in blue in the revised
manuscript.

We hope that with these modifications
the paper is found suitable for publication in the {\it International Journal of Heat and Mass Transfer}.

\clearpage

\section*{Referee 1}
\begin{enumerate}[leftmargin=*,itemsep=24pt]
\item \textbf{Comment 1}

\end{enumerate}

%\bibliographystyle{unsrt}
%\bibliography{REFER}

\end{document}

### 2018-07-04 Paper/sense.tex
..

As discussed earlier in Section~\ref{sec:intro}, bulk thermal conductivity estimates in NEMD
are dependent on the choice of the inter-atomic potential as well as values associated with
the individual potential parameters. In the case of silicon, the Stillinger-Weber inter-atomic potential
has been used for a wide variety of 
systems~(see~\cite{Laradji:1995,Zhang:2014,Jiang:2015,Watanabe:1999,Zhou:2013} and references therein).
However, according to Stillinger and Weber, the set of nominal
values as provided below in Table~2 were based on a constrained search in the 7D parameter space
to ensure structural stability and agreement with the available experimental data~\cite{Stillinger:1985}.

>>>>

As discussed earlier in Section~\ref{sec:intro}, bulk thermal conductivity estimates in NEMD
are dependent on the choice of the inter-atomic potential as well as values associated with
the individual potential parameters. In the case of silicon, the Stillinger-Weber (SW)
is a commonly used inter-atomic potential~(see~\cite{Laradji:1995,Zhang:2014,Jiang:2015,Watanabe:1999,Zhou:2013} and references therein). \rev{Functional form of the SW potential is given as follows:
%
\be
\Phi = \sum\limits_{i,j(i<j)}\phi_2(A,B,p,q,\alpha)\hspace{1mm}+\sum\limits_{i,j,k(i<j<k)}\phi_3(\lambda,\gamma)
\ee
%
where $\phi_2$ and $\phi_3$ represent two-body and three-body atomic interactions 
respectively~\cite{Stillinger:1985}.}

Although the SW potential is used for a wide variety of Si systems, 
according to Stillinger and Weber, the set of nominal
values as provided below in Table~2 were based on a constrained search in the 7D parameter space to ensure structural stability and agreement with the available experimental data~\cite{Stillinger:1985}.

### 2018-07-04 Paper/setup.tex
..

In this work, non-equilibrium molecular dynamics (NEMD) simulations are performed using the 
LAMMPS~\cite{Plimpton:2007} software package.
Essentially, a thermal gradient is applied by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
as shown using a schematic in Figure~\ref{fig:setup}.

@@

\begin{table}[htbp]
\begin{center}
\begin{tabular}{|c||c|}
\hline
Lattice Constant, $a$ ($\angstrom$) & 5.43 \\ \hline
Width, Height ($\angstrom$) & 22$a$ \\ \hline
$\Delta t$  (ps) & 0.0005 \\ \hline
Boundary Condition & Periodic \\ \hline
Lattice Structure & Diamond \\ \hline
Inter-atomic Potential & Stillinger-Weber \\ 
\hline
\end{tabular}
\end{center}
\label{tab:input}
\caption{Set of inputs for the NEMD simulation to estimate thermal conductivity in a Si bar using LAMMPS.}
\end{table}

>>>>

In this work, non-equilibrium molecular dynamics (NEMD) simulations are performed using the 
LAMMPS~\cite{Plimpton:2007} software package.
Essentially, a thermal gradient is applied by means of \rev{Langevin} thermostats located
at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
as shown using a schematic in Figure~\ref{fig:setup}.

@@

\begin{table}[htbp]
\begin{center}
\begin{tabular}{|c||c|}
\hline
Lattice Constant, $a$ ($\angstrom$) & 5.43 \\ \hline
Width, Height ($\angstrom$) & 22$a$ \\ \hline
$\Delta t$  (ps) & 0.0005 \\ \hline
\rev{Simulation Run Length (ps)} & \rev{320} \\ \hline
Boundary Condition & Periodic \\ \hline
Lattice Structure & Diamond \\ \hline
Inter-atomic Potential & Stillinger-Weber \\ 
\hline
\end{tabular}
\end{center}
\label{tab:input}
\caption{Set of inputs for the NEMD simulation to estimate thermal conductivity in a Si bar using LAMMPS.}
\end{table}
